Implicit Neural Representation for Potential Field Geophysics

### 2023-10-12 paper2.tex
Final tweak for first submittable draft

\begin{landscape}
    \begin{figure}[hbtp]
        \centering
        \includegraphics[width=1\linewidth]{fig/p2/srcomp_14.pdf}
        \caption[Super-resolution geophysics grid results I]{Super-resolution predictions on open access data, prepared using the proposed method.
            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.
        }  
        \label{fig:srdata14}
    \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[hbtp]
        \centering
        \includegraphics[width=1\linewidth]{fig/p2/srcomp_17.pdf}
        \caption[Super-resolution geophysics grid results I]{Super-resolution predictions on open access data, prepared using the proposed method.
            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.
        }  
        \label{fig:srdata17}
    \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[hbtp]
        \centering
        \includegraphics[width=1\linewidth]{fig/p2/srcomp_18.pdf}
        \caption[Super-resolution geophysics grid results I]{Super-resolution predictions on open access data, prepared using the proposed method.
            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.
        }  
        \label{fig:srdata18}
    \end{figure}
\end{landscape}

>>>>

\begin{landscape}
    \begin{figure}[hbtp]
        \centering
        \includegraphics[width=1\linewidth]{fig/p2/srcomp_14.pdf}
        \caption[Super-resolution geophysics grid results II]{Super-resolution predictions on open access data, prepared using the proposed method.
            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.
        }  
        \label{fig:srdata14}
    \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[hbtp]
        \centering
        \includegraphics[width=1\linewidth]{fig/p2/srcomp_17.pdf}
        \caption[Super-resolution geophysics grid results III]{Super-resolution predictions on open access data, prepared using the proposed method.
            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.
        }  
        \label{fig:srdata17}
    \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[hbtp]
        \centering
        \includegraphics[width=1\linewidth]{fig/p2/srcomp_18.pdf}
        \caption[Super-resolution geophysics grid results IV]{Super-resolution predictions on open access data, prepared using the proposed method.
            a) Ground truth, b) High-resolution, c) Low-resolution, d) Baseline super-resolution, e) Fine-tuned super-resolution, full explanation in-text.
        }  
        \label{fig:srdata18}
    \end{figure}
\end{landscape}

### 2023-10-12 paper3.tex
Final tweak for first submittable draft

\Cref{fig:grid40} shows the INR queried at \(z=\qty{40}{\m}\), which is the nominal terrain clearance of the survey.
A good qualitative match is achieved between the GA reference grid and the grid queried from the implicit representation, which successfully reconstructs the linear dune features and circular rim features.
This high performance is quantified by the residuals and peak signal to noise ratio (PSNR) of \qty{39.97}{\dB}, with mean residuals of \qty{0.4} and \qty{0.8}{\nano\tesla\per\m}
% Further level grids from other survey extents are included in Appendix A.

@@

\begin{landscape}
    \begin{figure}[hbtp]
        \centering{}
        \includegraphics[width=1.0\linewidth]{fig/p3/P864_dh_comparison.pdf}
        \caption[Horizontal derivatives]{Horizontal gradients calculated using the proposed method and the reference numerical method.
            Both numerical differentiation (left column) and AD INR (middle column) are calculated on the INR level grid or INR respectively.
            Residuals are calculated between the numerical and AD gradient grids (right column).}
        \label{fig:horigrad}
    \end{figure}
\end{landscape}

\begin{figure}[hbtp]
    \centering{}
    \includegraphics[width=0.9\linewidth]{fig/p3/P864_dv_comparison.pdf}
    \caption[Vertical derivative]{Vertical derivative grids queried from AD differentiated INR (left) and calculated numerically (right) on the \qty{40}{\m} level grid queried from the INR\@.
        The proposed method has poor vertical gradient representation, possibly due to the single height sampled in aeromagnetic survey design.}
    \label{fig:vertgrad}
\end{figure}

>>>>

\Cref{fig:grid40} shows the INR queried at \(z=\qty{40}{\m}\), which is the nominal terrain clearance of the survey.
A good qualitative match is achieved between the GA reference grid and the grid queried from the implicit representation, which successfully reconstructs the linear dune features and circular rim features.
This high performance is quantified by the residuals and peak signal to noise ratio (PSNR) of \qty{39.97}{\dB}, with mean residuals of \qty{0.4} and \qty{0.8}{\nano\tesla\per\m}.
% Further level grids from other survey extents are included in Appendix A.

@@

\begin{landscape}
    \begin{figure}[hbtp]
        \centering{}
        \includegraphics[width=0.8\linewidth]{fig/p3/P864_dh_comparison.pdf}
        \caption[Horizontal derivatives]{Horizontal gradients calculated using the proposed method and the reference numerical method.
            Both numerical differentiation (left column) and AD INR (middle column) are calculated on the INR level grid or INR respectively.
            Residuals are calculated between the numerical and AD gradient grids (right column).}
        \label{fig:horigrad}
    \end{figure}
\end{landscape}

\begin{figure}[hbtp]
    \centering{}
    \includegraphics[width=1\linewidth]{fig/p3/P864_dv_comparison.pdf}
    \caption[Vertical derivative]{Vertical derivative grids queried from AD differentiated INR (left) and calculated numerically (right) on the \qty{40}{\m} level grid queried from the INR\@.
        The proposed method has poor vertical gradient representation, possibly due to the single height sampled in aeromagnetic survey design.}
    \label{fig:vertgrad}
\end{figure}
